Title Goes Here

### 2020-02-24 paper/paper.tex
Basics of tail recursion representation in expression language
Better wording
Format 'TODO'

\subsection{Connection to Church encodings}
TODO: Write this subsection

@@

>>>>

\subsection{Connection to Church encodings}
\begin{tcolorbox}
  \textbf{TODO}: Write this subsection
\end{tcolorbox}

@@

\section{Representing tail recursion}
\begin{tcolorbox}
  \textbf{TODO}: Expand this section
\end{tcolorbox}

\begin{lstlisting}
data Iter a b = Step b | Done a
  deriving (Functor, Generic)

runIter :: (ERep a, ERep b)
  => (a -> Iter b a)
     -> (a -> b)
runIter f = go
  where
    go x =
      case f x of
        Done r  -> r
        Step x' -> go x'
\end{lstlisting}

In the \ttt{E} type, this is used to represent tail recursion by
the following constructors:

\begin{lstlisting}
data E t where
  ...
  StepExp :: E b -> E (Iter a b)
  DoneExp :: E a -> E (Iter a b)

  TailRec :: (ERep a, ERep b)
               => E (b -> Iter a b)
                  -> E (b -> a)
  ...
\end{lstlisting}
